---
format: html
filters:
  - rich-iannone/quarto-email
resource_files:
  - .output_metadata.json
attachments:
  - attach1.txt
  - attach2.txt
embed-resources: false
resources:
  - attach1.txt
  - attach2.txt
---

```{r setup}
library(tidyverse)
```

## A fancy report

::: {#unrelated}
This is an unrelated div.
:::


Hello

```{r}
#| echo: false
write.csv(iris, "attach1.txt", row.names = FALSE)
write.csv(iris, "attach2.txt", row.names = FALSE)
```

This is the final paragraph before the email portion.

::: {.email}

::: {.subject}
This is a subject.
:::

Here is some **R** code, which is contained within a code chunk. It produces a plot.

```{r diamonds_plot}

diamonds %>%
  group_by(carat, cut) %>%
  summarize(mean_price = mean(price)) %>%
  filter(cut != "Fair", carat < 3) %>%
  ggplot() +
  geom_point(aes(x = carat, y = mean_price)) +
  stat_smooth(
    aes(x = carat, y = mean_price),
    method = "gam"
  ) +
  facet_wrap(facets = vars(cut)) +
  labs(
    title = "Diamond Prices",
    subtitle = "Faceted by Diamond Cut",
    caption = "Source: The [diamonds] dataset in {ggplot2}.",
    x = "Carats", y = "Mean Price, US Dollars"
  ) +
  scale_y_continuous(labels = scales::dollar)
```

Nice figure up above. Let's make a second figure.

```{r mtcars_plot}
mtcars %>%
ggplot(aes(x = wt, y = hp, col = am)) +
geom_point() +
geom_smooth() +
coord_cartesian(xlim = c(3, 6))
```

This is an excellent second figure.

The following code will produce a tibble.

```{r dallas_home_sales}
dallas_home_sales <- 
  txhousing %>%
  filter(city == "Dallas") %>%
  group_by(year) %>%
  summarize(total_sales = sum(sales, na.rm = TRUE))

dallas_home_sales
```

And that is it for the email.

:::

This is the final paragraph in the document.
